### 2009-04-03 talk/icooolps2009-dotnet/intro.tex
minor fixes
Typos.

Finally, the low-level control flow-graphs produced by the toolchain
can be translated to executable code for a specific platform by a
corresponding backend.
Currently, three fully developed backends are available to produce
executable C/POSIX code, Java and CLI/.NET bytecode.

@@

The new generated code is potentially different for each run-time value seen.
This implies that the generated code needs to contain some sort of updatable
switch, or \emph{flexswitch}, which can pick the right code path based on the
run-time value.  Typically, the value we switch on is the runtime dynamc type
of a value, so that the JIT compiler has all information needed to produce
very good code for that specific case.

@@

>>>>

Finally, the low-level control flow graphs produced by the toolchain
can be translated to executable code for a specific platform by a
corresponding backend.
Currently, three fully developed backends are available to produce
executable C/POSIX code, Java and CLI/.NET bytecode.

@@

The new generated code is potentially different for each run-time value seen.
This implies that the generated code needs to contain some sort of updatable
switch, or \emph{flexswitch}, which can pick the right code path based on the
run-time value.  Typically, the value we switch on is the runtime dynamic type
of a value, so that the JIT compiler has all information needed to produce
very good code for that specific case.

@@

\anto{XXX: mention virtuals/escape analysis?}
